Robust Bayesian Analysis of Causal Inference in Medical Diagnosis and Treatment

### 2024-08-02 JASA-template.tex
Fix.

\added{In case 1, we consider an} increasing number of observations. \added{We} have two
sub-cases: in \added{case 1a} we consider all active variables to be confounders
and in the second \added{case 1b} we consider some active variables which are only related to
the outcome model. 
\begin{description}
    \item[\added{Case} 1a] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
    \item[\added{Case} 1b] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
\end{description}
For both \added{case 1a and 1b}, we consider different numbers of observations $n$ where
$n=25+ 5k$ for $k=0,1,2,\dots,25$ and $p=50$
predictors. This way, we check the efficiency of our method with varying level of information.

>>>>

\added{In case 1, we consider an} increasing number of observations. \added{We} have two
sub-cases: in \added{case 1a} we consider all active variables to be confounders
and in \added{case 1b} we consider some active variables which are only related to
the outcome model. 
\begin{description}
    \item[\added{Case} 1a] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
    \item[\added{Case} 1b] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
\end{description}
For both \added{case 1a and 1b}, we consider different numbers of observations $n$ where
$n=25+ 5k$ for $k=0,1,2,\dots,25$ and $p=50$
predictors. This way, we check the efficiency of our method with varying level of information.
